\hypertarget{actions-and-consequences}{%
\chapter{Actions and Consequences}\label{actions-and-consequences}}

``He what?'' asked Lex. He gripped the phone closer to his ear, though
that wouldn't help with the poor connection. It was moments like this
that made him want to revolutionize the entire telecommunications
industry. An investment of a million dollars would surely be enough to
get clear audio between Metropolis and Hub City. Of course, the world
was filled with such problems waiting for the right solutions, and
pushing things along too quickly was a waste of money more often than
not.

``He killed William Calhoun, sir,'' repeated Mercy.

``Who knows?'' asked Lex.

``Everyone, sir,'' replied Mercy. ``It happened just outside the
courthouse after the not guilty verdict was handed down.''

``I had hoped they would find him guilty,'' said Lex. His voice was
tight. Mercy was supposed to take care of things in Metropolis while he
was in Hub City. This was the very first time in their long association
that she had failed him, and either that meant she was slipping or
someone powerful was working against her. Both were worrying.

``I know sir,'' replied Mercy. ``I'm still trying to find out what
happened.''

Lex thought for a moment. ``I'll fly home later today,'' said Lex.
``Whatever is happening there needs my attention.''

He hung up without waiting for a response. Early on he'd made a
classification scheme for the most probable scenarios involving
Superman, and so far as he could tell, this was somewhere between class
C and class E. Superman had killed in a public way, which might signal
any number of things: a simple rash decision, a campaign of lethality
against the criminal element, or the opening moves of tyranny. Superman
had given no indication that he knew what Lex was doing, and Lex was
highly unlikely to get caught in the cross‐fire, which was the important
thing for now.

The estimated deaths from a class E scenario were in the thousands, and
while there would be severe economic effects, it was nothing that
couldn't be weathered in the short term. Hopefully the short term would
be all that Lex would need. In fact, a class C scenario might be of some
benefit. If Superman had only killed because he had momentarily snapped,
it was possible it would make the other scenarios less likely, depending
on which model of his psychology was correct. People were hard to
predict though, especially those with alien psychologies and a penchant
for lies. Scenarios of class J and higher involved the effective
obliteration of the human race in some way, but so long as Lex Luthor,
his stores of knowledge, and the spaceship were all safe, it was still
possible that Superman might yet be killed, which meant that anything up
to the murder of a hundreds of millions might still allow humanity to
survive.

He still didn't know how kryptonite worked, or what, precisely, it did.
The use of lead as a shield implied radiation of some kind, in addition
to the radiation of green light that gave it the distinct glow. He'd
taken copious notes and photographs as he'd taken apart the ship, and
while the kryptonite definitely seemed to be a power source, it wasn't
clear how that power was generated or harnessed. Lex had made no attempt
to activate the ship, and had no real plans to do so until after
attempts at using kryptonite as a weapon had failed, and then only after
careful consideration of the risks and dangers. The piece of the ship
that seemed to be an engine would be left alone for the foreseeable
future; anything with the power to exceed the speed of light or even
achieve a reasonable fraction thereof was a de facto weapon of
unconscionable power.

The kryptonite was in a solid block that must have weighed nearly twenty
kilograms, which was wholly inconvenient. Lex was hesitant to split it
up into smaller pieces, in the event that doing so would interfere with
its use as a power source for the ship, though at least the lack of
internal padding and shock absorbers suggested that this wouldn't be
dangerous. It was possible that kryptonite by itself held no harm at all
for Superman, and that kryptonite was only dangerous when the ship was
powered on and using the no‐doubt immense amounts of power that
interstellar travel required. Lex had settled for doing experiments on
the exposed surface of the core of kryptonite.

The lead tube that contained the kryptonite was itself surrounded by a
box of lead that Lex had constructed to provide for shielding. He
carefully lifted a cage out from the box, and peered at the rat that had
been living on top of the kryptonite for the past three days. A quick
dissection confirmed what a physical examination had suggested; the rat
was no worse for the extended exposure. When Lex was finished, he tossed
the corpse into a wastebasket with a frown.

Whatever kryptonite was emitting besides light was essentially invisible
to every tool that Lex possessed, but Superman's amazing powers
suggested that there were many aspects of physics that humanity had not
yet discovered. Lex made a snap decision. He put on a pair of thick
gloves and pulled the leaden tube from the box he'd built, and then
carefully pulled the block of kryptonite out of the tube. It came free
on the first attempt with a slight click. The spaceship had proven
remarkably easy to take apart once Lex had gotten to know the tricks to
its design, and he was confident in his ability to put it back together
again. Whoever had built it was an engineer of the highest caliber who
had designed it with serviceability in mind. He was being more risky
than he would normally have been, but time was not on his side.

It cleaved cleanly when he tapped at it with a hammer and chisel.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

Floyd had a bedroll, a pillow, a bucket filled with his excrement, a can
opener, a large amount of tinned food, and a rain barrel that Superman
refilled every few days. It wasn't much to fashion an escape with. The
hole was three hundred feet down, and curved slightly at the top to keep
rain or snow from getting in. The rock had been smashed through by
Superman, leaving what looked like easy handholds, but a single slip
even halfway up the hole would surely result in death. It was,
unfortunately, wide enough that Floyd couldn't brace himself against
both sides without stretching, which meant it would be difficult to get
a real rest. He looked up the hole for the third time in as many
minutes, trying to plot out a route and not think about how dangerous
and futile the climb was going to be. After he escaped out the hole, a
jaunt through the wilderness and certain recapture would be waiting for
him. He'd just about worked up the nerve to make the first jump up when
Superman came down through the hole, moving at speed.

The blast of wind flung everything into the air, including Floyd. Before
he even had time to react to his meager possessions being slammed
against the walls of the room, a solid hand was against his throat,
pinning him in place. Superman's eyes blazed with anger, and he pulled
back a fist. Floyd flinched back, which under Superman's hand amounted
to little more than turning his head a half inch to the side. When no
impact came, he opened his eyes back up. Superman was breathing hard.
His face was still a mask of fury, and his fist still poised for the
punch. A long moment passed.

``Ykr frkr,'' Floyd tried to say.

A single tear rolled down Superman's cheek. Superman flung Floyd to the
side, and he landed in a heap with what felt like a number of broken
ribs. He coughed, not just because of the hit against the wall, but
because the bucket had been knocked over and suffused the air with a
foul smell. When Floyd looked up, Superman was gone again. Floyd had
been trying to say \emph{Your father}, a last ditch effort at saving his
own life. He had no clue whether it had made the difference. Superman
had wanted to kill him, but hadn't been able to bring himself to throw
the punch.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

Strangely enough, Lois felt better about Superman now that he was off
the reservation. The anticipation had been the worst part of it all, and
now that he had finally snapped, she found herself calm and focused. The
time for subtle manipulation and walking on eggshells had passed, and
that came as a relief. Actually dealing with a disaster was something
she could handle; it was worrying about the possibility of disaster that
had been destroying her. Or perhaps she was simply too numb to properly
feel dread anymore.

``You're telling me that Superman killed the last crime boss of
Metropolis in the middle of broad daylight, and you didn't get a picture
of it?'' asked Perry White. He leaned over his desk and laid his hands
down on either side of it, looking for all the world like he was about
to vault over the mess of paperwork and personally throw Jimmy Olsen out
of the building.

``I couldn't!'' said Jimmy. ``He was~--- he did it too fast! I took a
picture just before, and the cops started movin' people away just after
that, I swear!''

``Feh,'' said Perry. ``We'll have to send a runner to one of the other
papers and pay out the nose for a picture if we can, because I'm sure as
hell not going to be the only guy printing off extras without the blood
and guts, obscenity laws be damned.'' He turned to Lois. ``You're
getting this story written, right?''

Lois wore a skirt that hung down just past her knees and a white blouse.
Both were splattered with blood on the left side, marking a perfect
silhouette where she'd been standing behind another reporter. She'd
cleaned most of the blood and gore off her face with the sleeve of her
blouse during the taxi ride over, and she'd had to tip the guy extra for
the mess she'd left behind in his backseat, but that was so far down the
list of things to worry about that it might as well not have happened.

``Just tell me how many words,'' said Lois. ``I got the opening portion
of it written on the way over. `Local businessman William Calhoun was
murdered shortly after his not guilty verdict by none other than
---'\,''

``Change that to `Alien vigilante Superman murdered local businessman'.
Maybe add `allegedly' though I don't know how he'd contest that,'' said
Perry.

``We don't need to say alien, everyone knows he's an alien,'' replied
Lois. ``And vigilante is true but harsh, even given what happened. I
don't want to give people whiplash by shifting our position too
quickly.''

``You write it, I'll mark it up and get it to print,'' said Perry.
``You're both dismissed, this is a steaming pile of shit that's not
going to wrap itself up anytime soon. Clark is supposed to come back
today, and he should be able to take some of this off your hands
whenever his train gets in.''

Lois practically ran back to her desk and started typing away, getting
all of her thoughts out before doing a second pass to reduce it down to
something that people would actually want to read. The headline was the
most important part, and the picture after that, but Perry would be in
charge of both of those, so they didn't bear thinking about. Her
typewriter was her steadfast friend, and it clattered loudly as she
jammed down the keys. Lois often felt like she belonged behind a
typewriter. She would take what she'd heard and seen and turn it into a
narrative that people would consume, and eventually that would become
the version of events that people told themselves.

``You okay?'' asked Jimmy. He stood next to her desk, shifting side to
side uncomfortably.

``I'm fine kid,'' said Lois, her fingers never leaving the keys. She
paused a moment and looked down at her clothes. ``My favorite blouse got
ruined.'' She chose her words carefully, not implying any agency. She'd
been training herself to be a better liar and a more careful speaker,
and she could tell that today was going to be a test of that. ``If you
want to help me, and Perry's got nothing better for you, go grab me a
change of clothing from Hudson's. I've gotta be back out on the street
as soon as this is done.'' Lex was in Hub City, and though it wasn't
safe to speak on the phone, she at least needed to touch base with his
valkyrie of an assistant.

She went back to typing, just as fast as before. The big story was
Superman, not Calhoun, but she'd spent the whole day preparing to write
about the outcome of the trial and couldn't help but sprinkle in more
about the man who'd died. Calhoun had no doubt deserved it, especially
if he was the mastermind behind the bombings, but Lois wasn't going to
position herself as Superman's cheerleader. Luthor seemed to want her as
something of a sycophant, but he hadn't yet been able to bring her
around to his way of thinking. Instead, she planned to tell Superman he
was wrong in as persuasive and gentle a way as possible. Luthor could
have words with her later.

``Okay,'' said Jimmy. ``But~\===''

``Jesus Christ kid, are you still here? Go!'' said Lois. She shook her
head as he scurried away. Some people just didn't have what it took to
make it in the news business. The Daily Planet needed a photographer
that could stare down mutilated children and burned out homes. Jimmy
Olsen was a few months away from dropping out, by her estimation, though
she'd thought the same of Clark almost from the time he'd signed on.

She turned back to her article, and tried to focus on the facts. The
verdict of the trial had been a big surprise, and the article she'd been
expecting to write was about Calhoun's slow decline, peppered with his
personal history and an overview of the utter destruction of organized
crime in Metropolis. Calhoun's death~--- his murder~--- changed all
that. Now the story was about Superman, and his failure to live up to
the impossible ideals he had set for himself. It was a story that she'd
been wanting to write for a long time, but she tempered her language.
Superman wasn't going to get a free pass from her, but she would imply
disappointment rather than outrage. Hopefully she'd be able to have some
influence on what the people of Metropolis were talking about tomorrow
(and thus what Superman was hearing), though no doubt the radio was
already having its say.

She dashed off her second draft as quickly as she'd ever done in her
life, and ran it back to Perry's office. Most of the blood on her
clothes had dried from a bright red to a dark brown. She'd felt parts of
Calhoun's skull hitting her face, and thought that she might have a cut,
but the story was done, and that was what mattered. The bone that hit
her had stung, like when a car kicks up gravel that hits your shins,
only in this case the gravel was bone that had been crushed into tiny
pieces. A brief image came to her mind of Superman killing every
criminal in Metropolis, littering the streets with their bones, no piece
left larger than a key on her typewriter. The momentary imagery was
unwelcome. She turned her thoughts back to the matter at hand and
slapped the article down on Perry's desk.

``It's no use,'' he said with a frown. ``We got a gag order.''

Lois grimaced. ``From who?''

``\,`From whom', darling,'' said Perry. ``It came down from on high, in
fucking triplicate. First a call from the chief of police, then a call
from the President of the United States himself, then the only man I
really give a fuck about, our employer.''

``Who the hell do they think they're kidding?'' asked Lois. ``There were
a hundred witnesses, there were cameras all over the place, it must have
gone out over the radio almost the instant after it happened. They think
they're going to keep this quiet?''

``The radio stations went to dead air in about two seconds flat,'' said
Perry. ``Someone had a plan in place for this, or something like it. I
don't think they're trying to contain this thing, just to manage it in
the short term. I've got no idea what they're going to say to make it
better, but for now they're just trying to keep a small bit of control
on the situation. I don't really blame them.''

``This is bullshit,'' said Lois. ``Complete and utter bullshit.'' In the
back of her mind, she wondered whether Lex was behind it. So far as she
could tell, he enjoyed his grand gestures. Giant statues in the park,
vast murals along the side of the road~--- shutting down mass media in
Metropolis would be just his style. It was almost reasonable too, if it
would prevent panic in the streets of Metropolis.

``No argument there,'' said Perry. He leaned back in his chair and lit
up a cigar. ``I'll edit for you, and if they lift the embargo we'll run
the story quick as can be, but until then, maybe you better get yourself
home and cleaned up.''

Lois again looked down at her clothes. ``I already asked Jimmy to go run
and get some for me,'' she replied. ``I'll keep on writing in
preparation for when we're allowed to talk about it.''

When she got back to her desk, there was a note waiting for her, one
that she'd been expecting for the last half hour. She read it twice,
then steeled herself and headed on up.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

``Why'd you do it?'' asked Lois the moment she stepped onto the roof. Of
course Superman could hear her coming, and she could have asked the
question at any point during the walk up. No doubt if Superman was
coming to speak with her, he'd been watching and listening to her from
the moment that he laid the letter on her desk, and probably from the
moment Calhoun's body slumped to the ground.

Superman didn't respond to her immediately. He stood at the very edge of
the roof, and his cape twirled and billowed in the wind behind him. She
wondered whether he had planned it that way, to look more impressive. He
had a flair for the dramatic, and an eye for looking impressive.

``I was angry,'' said Superman.

Lois watched him. He kept his back to her, so that all she could do was
listen to his voice. ``You've been angry before,'' she said. The image
of Superman standing in a room with the three men who had taken the
Whitman children, waiting for the police to arrive, was so real to her
that she could almost believe she had been there. ``What made this time
different?''

``I've been thinking too much,'' said Superman. ``I've been angry too
often. He was saying all those hateful things, I just\ldots{} it wasn't
that I snapped, really. I didn't lose control. If I'd actually punched
him as hard as I could have, Metropolis would be a smoking crater. I was
standing there, hating him, and thinking about how much better the world
would be if he were dead. Not by my hand, necessarily, but if he'd had a
stroke right on the steps of the courthouse the world would instantly
have been a better place. And to be honest, I was thinking about how
satisfying it would be to kill him.''

Superman kept staring out over the city. Lois waited him out. ``I can
slow down time,'' he said finally. ``Not that, exactly, but my
perception of time can change when I need it to. I wouldn't be able to
catch bullets otherwise. Moving fast isn't enough, you have to think
fast and see fast in order to really make use of the power. When I
really push it, the world dims down and sounds are happening so slowly
that it's nothing more than a persistent drone. I can live out a day in
the pause between words when someone is talking. The world goes so black
I can't even see my nose in front of me. First the sounds become too
long and stretched out to make sense of, and then they stop
altogether.''

His cape flapped behind him. ``I must have spent three days thinking
about Calhoun while we stood there. `Truth, justice, and the American
way', those were his last words. I meditated on them. The State of New
York executed seventeen men last year, and I had a hand in catching
eleven of them. I had vowed not to kill, you understand. The first one
was William Vogel, who was convicted of murder. I watched him spasm in
the electric chair, and I felt like a coward. I could have killed him
faster and more humanely. When I killed Calhoun, he probably didn't even
have enough time to register that I was moving before his brain was a
thick paste.

``I once believed in redemption. I believed in the justice of the legal
system, and when it failed, as it often did, I would tell myself that it
wasn't my place to rush in headlong. I didn't want to be a shepherd of
sheep, I wanted humanity to stand on its own two feet. But when law and
morality contradicted each other, as they often did, I was left with the
cruel alternative of losing just a bit of my moral center or losing just
a bit of my respect for the law. It's like you said; if I had come to
America when slaves were being sold on those very docks, would I have
respected the law then?''

``I didn't mean~\==='' Lois began.

``No, I know,'' said Superman. ``I read the article you just finished
writing. I deserve worse than what you said. I'm just trying to
explain\ldots{} to explain how I got to where I am now.'' He took a
breath. ``I used to think that good was something that was defined by
actions. Don't lie, don't steal, don't murder\ldots{} I thought that if
you worked at it hard enough, you could make up a set of rules to
follow, and that would make you a good person. I think that's what my
father thought. But eventually I moved away from thinking like he did,
and tried to live my life by his values instead. Maybe it was okay to
lie, if it was for the greater good. Maybe it was okay to break the law,
if breaking the law resulted in the greatest good for the greatest
number of people. The change was so slow I barely even noticed it, and I
don't think I was fully aware that I was thinking any differently until
a few days ago. But it didn't really matter, because for the most part I
was living my life the same way. Even if I no longer believed in an
absolute prohibition against killing~--- and how could I when I was
sending men to their death at the hands of the state~--- I still
wouldn't kill because of what it would say to people. I wanted to be a
symbol for them.

``But as I was sitting in the pitch black of slowed down time, I kept
thinking about truth and justice. I'd ensured that Calhoun would have a
fair trial, because I'd promised him he would. What would it say though,
to have him walk free? Not just from that trial, but from the botched
trial in December? He couldn't simply be immune to consequences. He had
to pay for his crimes. That was justice. I kept weighing these things
until I came to my decision, and it was only when my fist was halfway
through his skull that I realized my emotions had their thumb on the
scale.''

``What now?'' asked Lois after a long stretch of silence.

``I need to take time off,'' said Superman. He turned to face her. ``I
know you'll think I'm a monster for it~\===''

``I don't~\===''

``Lois, I know you better than you think I do,'' said Superman. ``I'm
going to take some time off from listening to the vast suffering that I
can only make a small dent in. I'll take time for myself and think on
what I really want to be. I fully expect that you'll hate me for it, but
I can't rush things and make mistakes, not when I have the power to
level mountains.''

Lois stared at him, then nodded. ``I won't hate you for it, but I can't
claim that I understand. If you think that taking some time off from
being Superman is what's best\ldots{}'' She sighed. ``I'll be here for
you when you come back. We all will.''

Superman stepped forward and kissed her on the cheek. He was off in the
air before she could formulate a response to that. He'd said he knew her
better than she thought, but she didn't know what the hell that was
supposed to mean.

He didn't want to be a shepard to the sheep. There was something about
that phrase that bothered her. It sounded familiar. She'd retained
enough knowledge of the Bible to recognize it as an allusion. It was
another way in which Superman showed a solid grasp of the culture he'd
married himself to, not just idiomatically correct English far beyond
what any foreigner learned, but cultural allegory. Certainly Superman
had been compared to Christ on enough occasions for him to recognize it,
but there was something else that made it stick out. It was like
something Clark would say.

She was halfway down the utilitarian stairwell that led down into the
building proper when it struck her. It wasn't just the turn of phrase,
it was the entire conversation. Clark's father was a pacifist, she
remembered him saying that over drinks one time. In fact, save for the
fact that Superman hadn't once brought up religion, all those words
could have come from Clark's mouth instead. A long, slow turn from faith
in the goodness of humanity~--- that was the story of Clark's time in
Metropolis.

She remarked on the physical similarities a few times. It was almost
always a joke at Clark's expense. ``Hey Clark, you spend some time on
athletics and you might rival Superman.'' But you couldn't look at Clark
and actually think that he was much more than an oaf. He had hidden
depths, but those depths weren't nearly so deep that he could actually
be~--- that he could have~---

Lois sat down in the stairwell and put her hands on her knees. She was
trembling slightly. ``Some time off from being Superman,'' she'd said.
They had the same eye color, the same hair color, and close to the same
height. They had a similar infatuation with her, and Superman treated
her as familiar because\ldots{} because she was familiar to him. They'd
sat side by side for months before Superman had shown up. They'd talked
about almost everything under the sun while putting together their
stories, and they'd certainly read almost everything the other had
written.

She needed to make notes, but Superman could watch her. Even now,
sitting in the stairwell, he was probably watching her and wondering
what she was thinking. Some distant part of her brain was telling her to
think up a cover, so she ran her hands through her hair and muttered
``He really did deserve it.'' Calhoun would provide a cover while she
tried to work through every conversation she'd ever had with Clark Kent.

She remembered Clark flinching when she'd said something\ldots{}
something about Superman not being totally emotionless when he came
across a scene of brutal violence. Clark hadn't been flinching because
he was a naive Midwestern farm boy, he'd been flinching because he'd
been \emph{remembering.} He was unreliable because he had other
obligations. He wasn't lucky, he was able to see through walls and
listen in on conversations that happened on the other side of the city.
He used a lot of unnamed sources. He covered Superman's trials. The span
of the deception that it would have required was breathtaking, shocking
enough that Lois had to remind herself to breathe. But it was true.

Clark Kent was Superman.

A thousand small details came sliding into context, and a hundred
questions followed in their wake. Lois clenched her hands into tight
fists. She could feel tears in her eyes. The biggest argument against
the theory was that she was \emph{smarter than that}, dammit, and if you
refused to believe something because it would mean that you were the
biggest idiot in the world, well, that alone said something about how
smart you really were. She'd been played. Clark Kent had lied to her
face for a year and a half, over and over. And Superman had done the
same.

``Calhoun deserved it,'' some small part of Lois remembered to say.
Superman was watching, always watching. And if he really was Clark, if
she hadn't simply gone insane\ldots{}

A few weeks after Clark Kent had first shown up in Metropolis, Lois had
taken a rare break from twelve hour days and gone out drinking. She'd
met a sailor at one of the dockside bars, and taken him back to her
place to do a few things that good Catholic women weren't supposed to do
outside of marriage. In the morning, she'd shoved him out the door and
gone into work. It would have been very hard to miss the fact that Clark
was in a bad mood, and that this bad mood was directed towards her.
She'd thought perhaps he'd seen her in the club while she was hanging
off the sailor's arm, and had simply pretended that she couldn't tell
what was bothering Clark. Now she had to wonder whether Clark was
watching her the entire time, or listening to that particular night of
passion. She'd imagined Superman's eyes on her frequently, and it was
never a pleasant thought, but if it was Clark watching her undress,
watching her with other men\ldots{} she could feel tears streaming down
her face.

There remained the question of why he would do it~--- why, if he had the
power to fly through the air and could crush coal into diamonds, he
would ever want to spend a single solitary second as Clark Kent. The
answer had to be that he was a monster. She flitted through her memories
of Clark Kent the reporter, and found one of him hunched over the
paperwork for his taxes. People had been dying, and he'd been
\emph{filing his fucking taxes}. He'd sat in on boring meetings about
style standards while people literally burned to death. And he'd lied to
her, over and over, every single day that they'd worked together. He'd
cheated his way to the top without any remorse. A cold fury ran through
her veins.

She stood up, wiped away her tears, and looked at herself in her compact
to assess the damage. Her hair still had blood in it, and that did
nothing for the effect. Lois did her best to fix what she could, then
smoothed out her skirt, took a deep breath, and walked out into the
newsroom.

Clark Kent was standing there, speaking with Perry. If she'd been less
angry, she might have run across the room to start beating him with her
fists, but she was far beyond that now. Instead, she gave him a weak
smile and sat down at her desk. There was no hiding that she had been
crying, but she could keep up a front for now.

``Are you okay?'' asked Clark as he sat down at his desk.

``Fine,'' said Lois. ``There's been a lot going on around here while you
were away. How was Smallville?''

``Small,'' replied Clark. ``I'd forgotten how small. My mother will be
missed. Listen, are you okay? I heard what happened, and I know you were
in the thick of it.''

``No, I'm not okay,'' said Lois. ``Are you back to work now? Because I
think I need to lay down for a while.''

``Sure,'' said Clark. He gave her a gentle smile that made her want to
stab him through the throat. He was Clark the deceiver, with a
sympathetic smile like he hadn't been the one to ruin her blouse with
Calhoun's blood.

Later, when she was safely at home, she took a shower and tried to keep
from imagining Clark staring at her with an infatuation that had once
been merely annoying. Clark Kent and Superman were both lies, and put
together they were an abomination of a person that pretended at
humanity. Lois could almost understand the anger that Calhoun must have
felt, and the desire to hurt the creature's feelings in lieu of being
able to damage his physical form. Lois wouldn't be so stupid as to give
into that temptation.

Instead, she would have to persuade Lex that something needed to be
done.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

Lex sat in his study, trying to keep himself as current as possible with
the newest developments in atomic research. His cover story for working
with kryptonite was that he was doing experimental work on a potential
weapon, and the best way to ensure that a deception was believable was
to make it real. Atomic weapons were certainly coming, and a worrying
prospect in their own right depending on how much power they would prove
capable of harnessing and how easy it would be to refine the necessary
materials. Lex had been quietly buying up uranium mines for a few years
now, but if the technology developed he had no doubt that he would end
up having to lock horns with the various governments that might lay
claim to them.

``Lois Lane to see you, sir,'' said Mercy.

``Wonderful,'' said Lex. ``Send her in, if you please.'' The study had
been cleaned of anything remotely incriminating before he left for Hub
City, and the atomic research was nothing that Lois would be able to
make sense of.

``It looks like we may have to cancel the book,'' said Lex as Lois
walked in. There was an actual book, with actual chapters, but it mostly
served as a plausible cover for passing notes to each other. Lex's
supposed role in the authoring of the book had grown as the months
dragged on, and now he was a full co‐author. Half of the time when they
spoke of the book out loud, it was in code. In this case `cancel the
book' had an equivalent meaning to `stop our covert attempts to
manipulate Superman's mental states'.

``Or at least write a new chapter,'' said Lois with a nod. ``Did you
read the paper this morning?''

``You spoke with Superman following his\ldots{} unfortunate decision,''
said Lex. ``And he'll be leaving us for a while.'' He wasn't sure how
much he believed it. Superman was a meddler by nature.

``Yes,'' replied Lois. She pulled a notebook from her purse, and began
writing on it. ``The book was always intended as a living book, but of
course we won't be able to release it with things as they are now, and
we don't want it to be obsolete the moment it hits shelves. I do have
some thoughts for what we'll need to change in light of this new
information though.'' She turned the notebook towards him. \emph{Is
there still no way to stop him?}

He watched her carefully. He had not, as yet, given her any rope to hang
him with. So far as she knew, she was the one in the lead, and Lex had
only used his immense resources in ways that conformed to the moral
standards of society.

``The science of Superman hasn't changed one bit,'' said Lex. ``Those
chapters will need the smallest amount of work, I should think. Public
reaction will need to be rewritten entirely.'' He made the hand signal
for \emph{No} in order to underscore his point, then the hand signal for
\emph{Why?}

``True,'' said Lois. She began to write again. ``I'd still like your
help, if you have the time. Even if Superman stumbles from time to time,
we can still use him as an example to live our lives by. Do you agree?''
She turned the pad towards him again, not missing a beat. \emph{Superman
has a secret identity that I am in close contact with. I need your help
in figuring out a way to stop him before he kills again.}

Lex very nearly froze. It wasn't what he had been expecting. He had long
thought that Superman or Clark Kent would eventually reveal the truth to
her, perhaps after she had taken the courtship with Superman far enough.
Lex had almost told her himself in order to prepare her, but it would
have opened up too many questions about how much he had known and for
how long.

``Certainly,'' said Lex. ``Though I'm not entirely sure that it's within
my area of expertise.'' He gave the hand signal for \emph{Tell me more}.
It was still too early to take any concrete actions, especially when
events were in flux, but he was already planning how he'd use Lois to
slip Superman the kryptonite.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Author's Note: Sorry about the delay. The next chapter should land
on July 19th, and will be the final chapter of this story.}

\emph{It usually goes without saying, but these characters have their
own views and biases which are distinct from my own.}

\emph{As always, I appreciate the favorites / follows / reviews.}
