\chapter{Finale, Part 2}\label{finale-part-2}

\emph{Dear Lois,}

\emph{I've been a longtime reader of your articles, and I have to say
that I'm quite the fan. I've been happy to note from the few photographs
I've seen of you that we seem to share a similar taste in fashion, and I
just wanted to share a tip with you. There's a jewelry store up on 18th
and 22nd called Marxhausen's, and they have just the most fantastic
pieces that would perfectly complement your outfits. Their necklaces are
so delicate and understated, just the thing for a woman like you. I
don't know if you have a special man in your life, but if you do I'm
sure he'd love to see you in it --- and if you don't, I'm sure that it
would help attract one!}

\emph{Your loyal fan,}

\emph{Lucille Lindt}

Lois got a number of letters from the citizens of Metropolis on any
given day. Lex had arranged for this to also be a private channel of
communication. The opening sentence was one she'd memorized, and if that
weren't enough, the initials at the bottom were L.L., initials that she
and Lex shared --- his idea of a joke, she supposed.

She went down to Marxhausen's over her lunch break, not really knowing
what to expect. She'd kept her distance from Lex ever since she and
Clark had hit the reset button on their friendship. If Clark had asked
her a direct question, she might have given up her last remaining secret
to him, but so far he hadn't shown any curiosity. That made her a bit
nervous. It was well possible that he'd already made his own deductions
on that score, especially if he'd been watching her. He knew that she
had a less than glowing opinion of him, and the book she'd written with
Luthor was damn near a hagiography, with none of the complexity that
she'd brought to her recent talks with Clark. But he hadn't asked, and
she hadn't felt like offering it up on her own.

The jewelry store was a small slice of glamour that didn't quite fit
with the rest of the block. It wasn't uncommon for the borders of the
neighborhoods to shift slightly over the years, and from what Lois could
tell, Marxhausen's had been the victim of one of these shifts. It was a
small, narrow store, staffed by a fetching woman with obscenely blonde
hair who perked up at the sound of the door opening. Lois looked around
slowly. There was nothing obvious to mark this as part of some plot.

``Can I help you?'' asked the blonde woman.

Lois took a breath, and dove right in. ``My name is Lois Lane, and I'm a
reporter for \emph{The Daily Planet}. My editor keeps asking me to write
a women's piece that's not about equal rights or social issues, and I
decided that I'd finally indulge him. So I was thinking that I would
write about jewelry. It should help pacify him, I think.'' Hopefully
Clark wouldn't think that was too suspicious. Lex had only gotten her to
the store, and she didn't have the barest outline of a script. Of
course, it would mean that she would have to actually write the article,
on top of her other work.

A sudden change came over the woman's face, her eyebrows falling and
then rising again, and when she spoke, her voice was slightly higher
than before. ``Oh, oh yes, there's so much that I could tell you about.
More and more women are buying their own jewelry these days, working
women who want to attract a husband.'' She reached beneath the counter.
``In fact, if you'd be willing to mention Marxhausen's in the article,
there's a piece I think you might like. It comes with a matching watch,
for that special man in your life.'' She had a nervous giggle.

She set two items down on the counter. One was a small golden locket,
shaped like an oval. The other was a watch, which glowed green behind
the clock face. Lois made no move to touch it.

``Is it radium?'' asked Lois.

``What?'' asked the woman with a puzzled look.

``Radium,'' Lois repeated. ``It's a metal that glows green, just like
that. Twenty years ago there was a group of factory workers --- women
--- who painted the faces of watches with radium so they'd glow in the
dark. They licked the tip of their paint brushes to get a fine point,
and they suffered from radiation poisoning --- anemia and bone
fractures, and then their jaws started to fall apart, disintegrating.''
She had literally written the book on it.

``I've, ah, been assured that it's safe,'' said the blonde woman.

``So were the girls who worked in the factory,'' said Lois. She wondered
how far she was deviating from what Lex had planned. Obviously she was
intended to walk out of the store with watch and the necklace. ``I'm
only curious about what makes it glow, I don't mean to be so \ldots{}
adversarial. The locket has a similar component?''

``Oh yes,'' said the saleswomen, who seemed grateful to be back on
familiar ground. She cracked the locket open, and showed a multi‐faceted
gem.

``Alright,'' said Lois. ``I'll take them. Now for this story, I have a
few questions \ldots{}''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\emph{What does it do?} wrote Lois.

Lex frowned at the notebook. He had thought that the next course of
action would be obvious to her: give Clark Kent the watch and see what
happens. He'd done his best to keep her out of the loop specifically so
that if Superman asked her, she would be able to tell the truth.
Superman had to know that there was someone plotting against him by now,
especially given the theft of the spaceship and the death of his mother,
but it was important that it appear as though Lois had been used as a
pawn, rather than the more valuable bishop or knight that she really
was. And then she'd had to go and ruin it by visiting him and asking for
answers, which would seem unacceptably suspicious.

\emph{I don't know}, Lex wrote back. \emph{I have reason to believe that
it will hurt him.}

Lois read the note and frowned at him. She tapped her pencil against the
paper for a few moments.

\emph{I'm not sure we should.}

Lex stifled a groan. He was losing Lois, that much was clear now. It was
at least gratifying to know that she hadn't taken leave of her senses in
coming to him; it was only a problem of a different sort. He could deal
with a question of loyalties, at least in the near term.

\emph{I figured out his identity,} wrote Lex. \emph{It wasn't difficult
once I started looking at the people around you.} He watched her face as
she read that, then took the notebook from her again before she had a
chance to respond. \emph{You're starting to feel sympathy towards him.
You think that you understand where he's coming from.}

Lois shrugged, then nodded. \emph{He's not perfect,} she wrote back.
\emph{But I think that I know where he's coming from now. We've been
talking a lot lately.}

\emph{He murdered a man in cold blood}, wrote Lex, but Lois was already
shaking her head.

\emph{He regrets it,} she wrote back.

\emph{What else will he come to regret?} asked Lex. \emph{We're talking
about the fate of the world. You know that there's no stopping him if he
goes rogue. Even if the chance is slim, it's a chance weighed against
the total destruction of humanity. If the odds are a thousand to one
that he'll kill us all, that's an average of two million dead. My own
estimates are higher, but you know him better than I do.}

Lois frowned. \emph{Will it depower him, or kill him?}

\emph{I don't know,} wrote Lex. He was halfway certain that she was
testing him. He would have pivoted, and claimed that he knew what the
effect was, but he'd already said that he didn't know, and couldn't take
the chance of getting caught in the lie. \emph{There is some element of
risk here, but I think it's low. The mineral in the watch emits a
radiation that I suspect will cause some interference with his power. I
need you to observe him carefully when you put the watch on him.} Lex
had done his own probability estimates, based on what he knew of
Kryptonian engineering from taking apart the ship. He strongly believed
that Superman's powers were of technological rather than biological
origin, simply given their raw power, and if kryptonite had any negative
effect at all, the engineering of the ship suggested to him that it
would have been designed to fail safely. Telling Lois that he'd weighed
the odds of catastrophe and found them acceptable would probably not
endear her to the plan though.

Lois slowly read what he'd written. She considered for a moment and
wrote back. \emph{You would be exposing yourself. Clark would know that
someone was aware of his secret identity --- someone besides me, if he
believed I was an innocent victim of your machinations.}

\emph{A risk I'm willing to take}, wrote Lex. Superman almost certainly
already knew. That ship had sailed after the Smallville operation. But
there wasn't a convincing lie that he could tell Lois to explain to her
how he had come by that information. If she were trustworthy, this whole
conversation would have gone a lot smoother.

Lois absentmindedly bit the end of the pencil and paced around the room.
Lex didn't know how she weighed the arguments, but if she refused him,
everything got much more complicated.

\emph{You still don't actually trust him,} wrote Lex. \emph{You would
have told him about our arrangement if you did.} He handed the pad of
paper to her, and she stared at it mutely.

Some time passed, but eventually she nodded.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Clark wasn't at his desk when Lois came into the office. She put the
necklace and the watch into the lead‐lined drawer of her desk, and tried
to get some work done. She'd been put in an awkward position by Lex.
Simply talking to Clark about how she felt had done wonders, and melted
away a good deal of her stress. He was still in love with her, and that
would have to be dealt with at some point in the future, but she'd
confessed her fears and frustrations and he had been understanding. They
had their disagreements --- deep disagreements that weren't going to go
away anytime soon --- but they were at least talking to each other like
reasonable adults.

Clark came in, hung his coat up on a hook on the wall, and took a seat
at his desk. He smiled pleasantly at her.

``I got you a gift,'' said Lois. Her voice nearly caught. ``Not that
much of one, really, since it was free, but I thought you might
appreciate it.'' She opened the desk drawer, and heard a noise from
Clark's desk. He was standing far away from her, with a serious
expression on his face. She hadn't even seen him move.

``There's a small box in my briefcase,'' said Clark. His voice was calm.
``I want you to take it out and put both the watch and the necklace in
it.''

``Clark,'' Lois began. Something had gone horribly wrong.

``Now, please,'' said Clark. ``Be careful, the box is heavy.''

Lois did as she was instructed. The box was a crude thing. It felt
heavier than it should have been. She put both the pieces into it, and
closed it tight. When she did, Clark strode forward and picked the box
up, then sat down in his chair. No one else around them seemed to have
noticed any of this.

``It seems that we were less than perfectly honest with each other,''
said Clark. ``Old habits, I guess.''

``Clark,'' said Lois. She folded her hands into her lap, to keep them
from shaking. ``Fuck, I don't know what to say.''

``Language,'' said Clark with a mild tone. ``I'm not angry, just
disappointed. We'll have to talk this out later.'' He drummed his
fingers on top of the box. ``Just for my own personal confirmation
before I confront him, who gave you these?''

There was no way to deny it. Clark already knew. ``Lex Luthor,'' said
Lois. Her mouth felt dry.

Clark stood up from his chair, and tucked the box under one arm as
though it were weightless. ``Well, I'm off to have a talk with him.'' He
began to leave, as though nothing at all were wrong.

``Clark,'' said Lois. He stopped, and turned towards her. ``I'm sorry.''

``Well, that's a start,'' he replied. He gave her a heartbroken smile.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

``Superman to see you, sir,'' said Mercy.

Lex simply stared at her. Just once he would have liked to see some
trace of emotion from her, but Mercy could announce that the world was
ending and still seem like she was bored.

``Did he say what it was regarding?'' asked Lex.

``The fate of humanity,'' said Mercy, without so much as a raised
eyebrow or a polite cough to acknowledge the absurdity of it all.

``Ah, well, send him in,'' said Lex. He looked towards the lead‐lined
drawer of his desk, where a pistol with specially prepared bullets lay
waiting. Inside each lead bullet was a small sliver of kryptonite. It
was a terrible plan, so far as they went, but at least it was there.

Superman strode into the study, looking around as he went. He was
graceful, for someone so big. The bright colors of his costume clashed
with the rich mahogany and leather upholstery of the room, but he didn't
seem to notice or care.

``I don't believe we've had the pleasure of being introduced,'' said
Lex. ``I was an innocent bystander at a bank robbery that you stopped,
though I'm sure you don't remember my face. I'm Lex Luthor. I suppose
you already know that.'' He extended a hand, and when Superman shook it,
he tried not to think about his fingers being mashed into pulp.

Superman sat down in one of the chairs, and offered Lex a pleasant
smile. ``Well, I'm not sure quite where to begin.'' He looked around the
room for a moment, perhaps contemplating the fact that he was surrounded
by lead. Then he turned and pointed to bound proof on Lex's desk, a copy
of the book he and Lois had put together about Superman. ``May I?''

``Certainly,'' said Lex. ``If there's anything that you think needs
changing, we'd be happy to---''

Superman waved him off, and opened the sheaf of papers to somewhere in
the middle, finding what he wanted immediately. ``Ah, here we go. `The
currently accepted explanation for Superman's so‐called x‐ray vision has
nothing to do with x‐rays. Though one can be forgiven for thinking that
they have something to do with that particular form of radiation given
that both are used to peer through otherwise solid objects, as well as
the use of lead for shielding, the similarities end there.'\,'' Superman
looked up at Lex for a moment, then back down at the book. ``And so on
and so forth, and then here, this is what I wanted to point out.
`Superman's penetrative vision is thought by leading scientists to
utilize some hitherto unknown aspect of particle physics. The
hypothesized krypto particles permeate the universe and can pass cleanly
through every known element aside from lead.' And then it goes on to
talk about the difference between lead as it applies to x‐rays and lead
as it applies to krypto particles.''

Lex stared at Superman. He tried to keep calm and slow his heart rate
down. ``Are you telling me that you can see through lead?''

``No,'' said Superman. ``However, let me offer up a hypothetical. Let's
say that there's a mineral that was found in the core of a meteorite.
Two separate research facilities were sent samples of the meteorite ---
not by me, but by a third party --- and they could find no form of
radiation using any of the instruments at their disposal. I know for a
fact that it does emit radiation, because as you seem to have guessed,
that radiation has an unsettling effect on me. As an additional piece of
information, the radiation from this mineral is blocked by lead, but
seemingly by nothing else. What do you suppose it would look like to my
x‐ray vision?''

``Bright,'' said Lex. ``Because if it emits anything, Occam's Razor
would dictate that it's krypto particles rather than some distinct
particle which shares many of the same properties. And if they're the
same, it's a matter of degree --- the mineral emits far, far more than
you use to see by.'' He should have seen that possibility far, far
sooner. The only question remaining was how many layers of deception it
would allow Superman to peel back.

``It's as bright as a blazing sun, difficult to look at directly when
I'm using my x‐ray vision,'' said Superman. He shrugged. ``I probably
would have been able to piece it together all the same. A man walked by
me with a piece of glowing green rock in his breast pocket, and I felt
myself grow weaker. It got worse the closer he got. I have extensive
practice at faking reactions, or faking a lack of reaction, and just
when I was beginning to feel mortal, and worried that I was going to be
killed in some ignoble way, he kept on moving by. So I held myself in
check, and as soon as I got to a safe place, I looked through the walls
and watched him. I saw a piece of rock that was so bright it nearly
blinded me.''

Lex kept very still. The research facilities he'd sent the kryptonite to
hadn't had lead shielding, and he hadn't thought that they would need
it. The story he'd given for the appearance of kryptonite had been
solid, and the forged paperwork had been airtight. Experimentation and
synthesis of an unknown mineral shouldn't have been suspicious ---
except that Superman would only have had to go to space and look down at
the planet. If they shone as brightly as he claimed they did, they'd
stick out like a sore thumb.

``So,'' said Superman. ``I stole a piece of the PU‐356 from one of the
labs. I won't bore you with the details, but it would suffice to say
that I can see through walls and move as fast as I want to, which makes
me an excellent thief. I confirmed that it could hurt me, and after that
it was just a matter of being careful until I could confirm your
involvement to my satisfaction. I'm not in any real danger from the
PU‐356, though it is inconvenient. I can see it clearly from miles away
without having to try all that hard, and my superior speed means that a
bullet made of it could never hit me.'' Superman sighed. ``Of course, we
can drop the pretense of there ever being a meteorite. That would be too
big of a coincidence to swallow, if a meteorite capable of harming me
was found and put into mass synthesis just a short while after my
spaceship was stolen from me.''

Lex's mouth felt dry. ``I was blackmailed,'' he began. ``I was told that
unless I tried ---''

Superman waved his hand. ``I don't believe you,'' he said with a half
smile. ``You made a good faith attempt to kill me, and you used Lois to
do it.''

``The military ---'' said Lex.

``There were a few reasons that I came here,'' said Superman. ``Things
we need to discuss. First, I want you to admit to what you've done. All
of it.''

Lex's face fell. ``I don't know what it is you think you know,'' he
said. ``Or how you think you know it. I did arrange for Lois to deliver
a piece of the mineral to you, and it was an attempt to see whether you
could be disrupted in some way, but I don't know anything about a
spaceship. So far as I'm aware, it burned up on re‐entry. I felt it
prudent to have a method of dealing with you in case the worst were to
happen, and I can only hope that ---''

``Towards the end of his life, William Calhoun talked a lot,'' said
Superman. ``He sat in a jail cell, and if prayer is an expression of
love, then he did whatever the opposite of praying is. Some of what he
said was nonsense, credit taken for crimes that he didn't commit, but I
could usually tell by how he spoke. He wasn't the guiding hand behind
Harry Kramer's bombing campaigns. If he had been, he would have brought
it up more often, instead of just in those moments that he really wanted
to twist the knife as hard as possible.''

``You think that I could possibly be behind that act of terrorism?''
asked Lex.

``It wasn't terrorism,'' said Superman. ``It was a series of attempts on
my life. Terror was only a byproduct. Given that I know you tried
earlier today, it's not unreasonable to think that you had tried
before.'' He held up a hand to forestall any objections. ``I'm less
certain about that one, and obviously I have no hard proof. Certainly
nothing that would hold up in a court of law. Still, it became clear
fairly early on that I was looking for someone who was intelligent and
possessed an enormous amount of resources. That you have lead‐lined
rooms in both your home and office, speak in languages other than
English for no good reason, and have a penchant for codes --- well, that
helped to paint a picture. I want a confession from you, one that covers
everything you're guilty of.''

``And then you'll kill me?'' asked Lex.

``No,'' said Superman. ``I'm willing to accept your unconditional
surrender.''

``Ah,'' said Lex. ``And what does that entail?''

``Part of an unconditional surrender is that you don't get to ask that
question,'' said Superman. ``I beat you. It's over. You have exactly one
thing that can give me the slightest injury, and I can see it coming
from a mile away. I'm fairly certain I know how you think now. It's been
a learning experience, watching all of the machinations of an enemy with
nearly infinite resources and a steadfast refusal to be identified.''

``Fine,'' said Lex. It was time to change tactics, and concede some
ground in the hopes of arranging a more advantageous battlefield. ``I
confess. I was the one who figured out your inability to see through
lead, and allowed that fact to be known around the world. I arranged for
the bombs to be made and placed, knowing that innocent people would die.
I figured out your identity as Clark Kent, and inserted agents into
Smallville. Your mother's death was unintentional. I stole your
spaceship. I found a single small chink in your armor and tried my best
to use it against you. I believe that's an accurate list of my crimes.''
Almost all of the layers of deception had slid off now, with only a few
secrets still held back in reserve, more out of a faint sense of hope
than any coherent strategy. Lex felt naked.

``Why?'' asked Superman. He showed no shock or surprise.

``You are too dangerous to be allowed to live,'' said Lex. ``You cannot
be stopped after the fact, which means you must be stopped prior to
it.''

``Do you know why I killed Calhoun?'' asked Superman.

``According to Miss Lane, you were angry with him,'' said Lex. He tried
not to be bothered by the seeming non sequitur. Superman was at an
advantage in not only strength and speed, but information as well. Lois
had said he had the ability to think for long moments in the space
between blinks, and perhaps that accounted for the disjointed
conversation. Or maybe Superman had just prepared a script for himself
to follow, and was sticking to the points he wanted to hit before he
brought Lex to a messy end.

``You're close,'' said Superman. ``I was angry with him, but anger alone
wasn't enough. Instead it was a chain of thought, with each step colored
in anger. I convinced myself that it was the correct thing to do, and
that wouldn't have been possible without the anger. I decided to kill
Calhoun, and then I worked backwards to figure out all the ways that I
could make that into the single best choice.'' He paused, and stared Lex
in the eyes. ``I've been looking over what I actually believe lately,
and trying to figure out why I believe it. And do you know, I think more
than anger, my thinking has been tainted by fear. As has your own.''

``Fear is a natural response to the chance of obliteration,'' said Lex.
``It's what saved our ancestors --- my ancestors, anyway --- from death.
When a new predator arrives in the woods, the appropriate reaction is to
run away or fight. There was no way to run away from you. So yes, I was
and am afraid of you, but that fear had a grounding in reality. I would
have acted the same even if I didn't feel an instinctive terror at your
presence on this planet.''

``I was good,'' said Superman. ``I was a paragon of virtue. I never hurt
anyone. I never acted in a way that was contrary to humanity. I never
interfered with politics or warfare. You feared me all the same, and
made it your mission to kill me. You got this idea in your head that I
was a threat ---''

``You were,'' said Lex softly.

``And you never stopped to reconsider whether that continued to be true
as time went on,'' finished Superman. ``I'm not a bad person. I can
understand if you had misgivings when I showed up, but as the months
passed, you never changed your mind, did you? Maybe you just didn't want
to admit that you killed all those people for nothing. You couldn't
admit you were wrong about me, because then you would be forced to think
of yourself as evil. Lex, I'm not going to destroy this planet, or
anyone on it. That's more true now than ever.''

Lex was silent. The issue wasn't whether Superman was planning to
destroy the planet, it was that he was capable of it at all. ``Knowing
what I know now, I would have done things differently,'' said Lex. ``But
up until an hour ago I thought it would be for the best if you were
dealt with, and you haven't said anything to change my mind. Regardless,
you have managed to convince me that it's not going to be possible to
accomplish that goal, so if you want my unconditional surrender, you
have it.''

``Good,'' said Superman. ``I said earlier that I had been ruled by my
own fears. They weren't fears of death or injury, for the most part.
They were fears of failing in other ways. I acted like I thought a hero
should act, and tried to be a symbol for people. I read your proposals
as they came out, and the proposals of others. Some of the ideas I'd
already thought of myself, while others were novel, but I had convinced
myself that part of being a shining symbol of hope, truth, and justice
was being static. Part of it was my father, I'm sure. He had his very
particular views about the world, and I was following his example. It
felt like I would have been turning my back on him if I'd decided that I
wanted to do things differently. And even when the evidence began to
grow that I'd been wrong --- or at least not completely right --- I
refused to change. I was afraid I would do something bad by trying to do
something good. I was worried that I would ruin our society, or mar
human history. I thought I would end up leading us down the same path
Krypton had traveled, letting too much happen too soon. It was logic,
tainted with the fear of failure. I had decided that I was going to keep
the world as it was, so that my responsibilities would stay small. Then
I rationalized my way towards that conclusion.''

``You're speaking in the past tense,'' said Lex.

``How much of what you've said over the past year was true?'' asked
Superman. ``How much do you want to make the world a better place?''

``I meant all of it,'' said Lex. ``I could have done much less than I
did, if I only wanted the appearance of philanthropy. I want to make the
world a better place.''

``That's what your surrender means,'' said Superman. ``You're going to
help me do the most good.''

``What's the catch?'' asked Lex. The important question of \emph{How?}
would come later.

Superman waved his hand around the room. ``No more lead. No more codes.
No more speaking in other languages. No more secrets from me. You'll
have to return my spaceship to me, and stop all of the current research
into a means of killing me. LexCorp will be turned into a machine for
generating good in the world instead of pure profit. I'll be doing large
scale labor, and you'll be managing the profits from that as well,
channeling them towards the areas where the money can do the most good.
I'll need a thorough debriefing on all of your methods of deception. It
probably goes without saying that I'll be watching you like a hawk. I
want your help in allowing me to keep my identity as Clark Kent secret,
which will likely involve buying \emph{The Daily Planet} and giving me a
list of everyone who you've told, for starters. And you're never to
speak with Lois again.''

``And if I don't want to take that option?'' asked Lex. He was already
thinking of ways to get around the restrictions that Superman was
talking about, but if the kryptonite was unworkable as a solution, it
was almost certain that the attempts on Superman's life would have to
stop for good.

``I'm going to build a prison,'' said Superman. ``You would be the
second inmate, if you refused. There would be absolutely no hope of
escape.''

``Then I'll help you, of course I will, but I'm afraid I still don't
understand,'' said Lex.

``I believe there's a goodness in you, Luthor,'' said Superman. ``I'm
still a Christian, and the story of the Bible is one of redemption. I
have nothing to fear from you, and you're in a unique position to effect
positive change. While I admit it would feel good to lock you away
forever, rehabilitation is more important than retribution. More
practically, no one knows of your crimes but me, and while I can prove
enough of it to my own satisfaction, I don't have any illusions that it
would hold up in any court of law. Making you disappear would raise
questions, and I don't know who might have the answers. I also know your
methods well enough to know that you probably have a dead man's switch
somewhere, and of course I worry about what might be in it. My existence
as Clark Kent is important to me, and I don't want to give it up unless
I have to. You're a smart man. You know I'm offering you a good deal.''

``You are,'' said Lex. He swallowed. ``It makes more sense to keep me
alive and work towards our mutual goals. You hadn't struck me as being
so level‐headed.''

``People change,'' said Superman. He blurred forward. The chair he'd
been sitting in slid backward three feet and fell over. He stood right
before the desk, towering over it. His expression was deathly serious.
``I feel like it goes without saying, but I could kill you in a
heartbeat. I don't like using the threat of force, but if you step out
of the very clearly defined lines we're going to set, I will throw you
right into a specially made cell in my jail. If you give me reason to
suspect that you're still a threat to me or anyone else around me, you
will simply vanish from the face of the Earth and never be heard from
again.''

``Understood,'' said Lex. He noted what Superman had said, and the very
specific wording the alien had used. He had not actually said that he
would commit murder, only that he could. And the threat of consequences
had been vague. Superman was back to being a pacifist, it seemed, after
a dalliance with murder. Lex could use that against him.

But then, perhaps it made the most sense to simply accept the reality of
Superman. If kryptonite shined brightly and Superman knew to look for
it, it would be nearly impossible to kill him with it. A kryptonite bomb
surrounded by lead would only work if Superman could be maneuvered
directly next to it, and as soon as he saw the casing of the bomb bowing
outwards he would be on the move. The other clear option was to get
Superman as he slept, but given what they both knew about each other,
there was a decent chance that Superman would simply stop sleeping, or
rotate through different anonymous locations --- and that was assuming
that Superman could even be snuck up on while he slept. If Superman knew
about kryptonite, and was willing to work outside of or in opposition to
the law, the problem seemed nearly unworkable.

``Which of the proposals did you want to pursue?'' asked Lex.

Superman stood back, and brushed off his costume. ``I'm looking for pure
efficiency, which is your area of expertise. You're going to spend the
next few days tearing the lead from these walls and complying with my
demands, and then I want you to start writing a proposal for how I can
do the most good. I won't kill anyone, and I want to try to keep my
interference with governmental bodies to a minimum, but I am willing to
reshape the world in any other way.''

``I'll think on it,'' said Lex.

``Don't cross me,'' said Superman. ``I'm hoping that you can see that
this is good for both of us.''

Lex nodded stiffly. All his preparations and all his caution had been
for nothing. This wasn't the end that he wanted, but it was the best
that he could have hoped for after his masks had been taken away from
him.

``This will be the last time we see each other in person,'' said
Superman. ``Or rather, the last time that you see me. I'll be watching
you.'' He turned to leave, then stopped and stared at the door. He
glanced back at Lex with a frown on his face, then looked at the door
again. It was lead of course, just like the walls of the room, but
something had given Superman pause. ``Miss Graves, please move away from
the door.''

Instead, the door to the study began to open, and it had shifted only
the smallest fraction of an inch in the time it took for Superman to
stand behind Lex's desk. He moved quickly and efficiently, being quite
delicate with his power. By the time the door swung open, Superman had
Lex's head in his hands, one of which was gripping his jaw. Lex felt no
sensation of pain or even discomfort, only firm hands. Mercy stood at
the doorway, with a solid block of kryptonite the size of a baseball
held straight out in front of her.

``Mercy, was it?'' asked Superman. His vice grip didn't let up for a
moment.

Mercy nodded.

``You have to know that this is utterly futile,'' said Superman. ``I
shouldn't have expected you to sit idly by while Lex and I had our chat,
but we've come to an agreement of sorts. I want to leave here peacefully
and with a minimum amount of destruction or loss of life.''

Lex's jaw was held firmly in place, preventing him from speaking. He
could only hope that Mercy would understand from the look in his eyes.
She took a half step closer.

``Stop,'' said Superman. She stopped. ``I'm going to let Lex speak to
you, to try to convince you that you should leave. Lex, consider this
your first test.''

Lex's jaw was gently released. He took a breath. ``Mercy, I want you to
listen to me very carefully. Throw the kryptonite towar---''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The grip on Lex's head vanished just as the wall behind him shattered
outwards with a rush of air. Mercy had started winding up for a throw
before Lex was halfway through his sentence, and the block of kryptonite
landed on the desk, where it slid across and fell to the floor at Lex's
feet. Lex ignored it and opened the lead‐lined drawer to pull out the
pistol.

He stepped out the hole in the side of his mansion, where it was a nice
and pleasant summer day. Superman was laying on the ground a hundred
feet away, covered by his red cape, and Lex took off towards him at a
dead sprint, trying his best to avoid the glowing green shards and bits
of lead that Superman had taken with him when he went through the wall.

When Lex was five feet away, he fired three bullets into Superman's
head. The sight of blood sent a wave of relief through him, and he
crouched down next to the body to catch his breath.

``I studded the walls with kryptonite,'' Lex said to the corpse. He kept
his eyes on the body, just in case it started moving. It as far from the
first dead person he'd seen, but the sight of it still sent a surge of
adrenaline through him. He wouldn't have been terribly surprised if he
had passed out or threw up.

After a half a minute had passed, Mercy came walking across the lawn to
join him. Her hair was in the same tight bun as always, and she
certainly didn't look like she'd just played an instrumental part in
killing a god. She carried the chunk of kryptonite in one hand.

``He had a great many options for dealing with that situation,'' said
Mercy. ``How lucky did we just get?''

``I haven't had enough time to work out the odds,'' said Lex. ``But he
didn't want to hurt either of us, even after everything I'd confessed
to. Leaving through the side of the room was probably what I would have
done. He must have scoped out the mansion before he came --- watched me
in my study whenever you opened the door, observed our patterns. I think
it would be safe to say that we won because we were lucky. Putting
kryptonite in with the lead was at the far edge of my most paranoid
preparations, and after the brush‐by I had thought that it wasn't strong
enough. I was actually angry about wasting the money.'' He ran his hand
across his bare scalp. ``He was too dangerous to let live.''

``I know, sir,'' said Mercy. She looked across the yard. They were
separated from their neighbors by a massive expanse of lawn and thick
shrubs, but the noise wouldn't go unnoticed. ``We should figure out what
sort of story is appropriate to this situation.'' She looked at where
Superman lay. ``We should also dispose of the body.''

She was right, but Lex was having trouble focusing. He had won. It had
been damned sloppy. He should have arranged for Mercy to do what she'd
done on her own anyway. It should have been a masterstroke. If he had
lured Superman into the room and sprung a trap, he would have felt more
of a thrill of victory. But as his thoughts moved back towards the
conversation he'd had with Superman, he could tell there was another
reason that he only felt hollow. There was a small seed of doubt. Lex
had made his choice, and made that choice for all of humanity. It wasn't
unreasonable to wonder whether that choice had been the right one.
Still, the seed of doubt couldn't be allowed to grow, not after the
choice had already been made.

``I don't know how much of our conversation you overhead,'' said Lex.
``But it didn't change anything. He was just too powerful to be allowed
to exist.''

Mercy only nodded.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

``Any word from Clark?'' asked Jimmy.

``No,'' said Lois. ``I wouldn't expect any letters from him.''

``He just left without saying goodbye though?'' asked Jimmy. ``I mean,
he was never very dependable, but I just didn't expect it of him.''

``He'd had too much of the city,'' said Lois. ``You read his letter of
resignation. He's back in Kansas, taking care of the farm. It wasn't
impossible to predict. You know how much he talked about Smallville.''
Lex had called her to let her know that Superman had been dealt with,
and the letter of resignation had come in the very next day. She'd been
feeling an awful pit in her stomach ever since, even as she tried to
keep Perry and Jimmy from asking too many questions. She had no idea how
Lex had done it, but she was certain that Clark was dead.

Jimmy moved closer and lowered his voice. ``The thing is, I was talking
to Eleanor. Did I ever tell you how we met?''

``At a bar?'' asked Lois.

``Right,'' said Jimmy. ``It was just after we'd gotten back from the
Whitman thing, and \ldots{} she asked me some questions about Clark. I
didn't think anything of it at the time, I was halfway to drunk and she
was --- is --- pretty much a goddess. Anyway, I was talking to her about
Clark's sudden retirement from the reporting business, and she broke
down and told me that it wasn't an accident that we had met each other.
I was part of a case she was working, to try to dig up some dirt on
local reporters. She works for a detective agency, and she thought that
maybe it was so that someone would be able to put pressure on him if the
wrong sort of story broke, but now \ldots{} now it seems a little
fishy.''

\emph{Luthor}, thought Lois. She should have known that after she told
him about Superman's secret identity he would try to find out more.
Maybe it had been one of the things that had tipped Clark off and let
him know that someone was on his trail. ``Wait a second, you started
dating after we covered the Whitman kidnapping?''

``Yeah, why?'' asked Jimmy.

The timeline didn't match up. She'd come to Lex months later, which
meant that either someone else was snooping into Clark's past, or Lex
had known the truth far before she had. One of those options seemed far
more likely than the other.

``Nothing,'' said Lois. ``You've just given me something to think
about.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Just because Superman was gone didn't mean that Lex could rest easy.
There was a possibility that more aliens would arrive at some point in
the future, and if they had capabilities anything like what Superman
had, humanity needed to undergo a rapid technological advancement as
swiftly as possible. Superman's spaceship still held a wealth of
information, and there was a piece of it that Lex thought of as its
brain --- a central component that was connected to all of the others
and likely carried signals of some sort. On top of that, there was the
brewing war in Europe to consider, along with the Sino‐Japanese
conflict. It was unfortunate that governments were more willing to spend
extreme amounts of money when there was an immediate danger to their
existence, but war --- or at least the threat of it --- would prove
useful.

``Miss Lane to see you,'' said Mercy. She had helped to drag Superman's
body from the wreckage and hide it in the trunk of one of his cars
before the police arrived, and as he might have predicted, the whole
experience didn't seem to have changed her at all. He was doing his best
to follow that example.

``Send her in,'' said Lex with a smile.

Lois looked different. She'd cut her hair aggressively short since the
last time they saw each other, and if she had always been a little bit
ferocious, now she seemed positively bristling.

``How much of it were you responsible for?'' asked Lois.

``I'm afraid I don't know what you're talking about,'' said Lex.

``You killed his mother, that much I'm nearly certain of,'' said Lois.
She sat down in what had been her customary chair, and stared at him
with intense eyes. ``I went out there, did you know that? I went to
Smallville, trying to find out who he had been. I'm surprised you left
so many loose ends. There was an autopsy report for Martha Kent that
didn't look right, and the day she died, when there was that big storm,
three people went missing from Smallville and never came back. They
didn't find bodies either.''

``Again, I have to insist that I don't know what you're talking about,''
said Lex. ``And if you're thinking of putting any of these thoughts to
print, I would suggest that you either have a substantial amount of
proof or a very, very good lawyer.''

``I kept thinking about the bombings,'' said Lois. ``Clark thought that
Calhoun was the man behind them, but he was wrong, wasn't he? While you
were putting out a reward for Kramer's capture in public, you were
sending him schematics and instructions in private. It wasn't possible
for a single man to have done it all, that much was obvious, so you
framed Calhoun and bombed your own properties to turn watchful eyes in
another direction. You were trying to kill Clark from the start.''

``Miss Lane, I generally make it a point to not bother refuting spurious
rumors about myself,'' said Lex. ``But given the gravity of what you're
suggesting and the fact that we were friends, once upon a time, I will
tell you completely and unequivocally that I had nothing to do with any
of that. I was a steadfast supporter of Superman ---''

``Because you needed a cover,'' said Lois.

``I was a steadfast supporter of Superman, and I was as disheartened as
anyone when he became a murderer and fled the planet,'' said Lex.

``You killed hundreds, didn't you, without even a thought for the value
of their lives?'' asked Lois.

``I am curious about what evidence drove you towards such a wild and
unfounded conclusion,'' said Lex. There was no way that she would be
able to prove anything.

In the worst case scenario, she had found the laboratory where the
spaceship was being kept and broken through all the layers of security,
but that still wouldn't be enough to implicate him in the public eye,
let alone the court of law. After the autopsy and a collection of
samples, Superman's body had been reduced to pulp, mixed with a healthy
amount of kryptonite, encased in lead, and lowered deep into an unmarked
grave on a vast, private nature preserve in Alaska which Lex had
exclusive control of. He had used hundreds of agents in the course of
tracking down and positioning Superman, but only a very few knew enough
to implicate an unknown master in wrongdoing, and only Mercy had the
ability to implicate Lex as that mastermind. It was well possible that
Lois could or would reveal to the world that Clark Kent had been
Superman, but it would have raised all kinds of questions he was sure
she would want to avoid, and either way wasn't something that could
really be proven after the fact --- nor would it substantially change
his plans.

``I don't have any evidence,'' said Lois. ``Believe me, if I did I would
be shouting it from the rooftops instead of coming here. You won,
Luthor. I just want to know what the hell you were thinking.''

``Well, of course I can't comment on things that I haven't done,'' said
Lex. ``If, hypothetically, I had engineered a series of heinous crimes
in pursuit of some foolish feud with Superman, I certainly would have
nothing to gain by telling you about my reasoning, especially not when
it would give more fuel to your paranoia.''

``I hated Clark for lying to me,'' said Lois. ``I hated him for living
this double life and pulling the wool over my eyes. But at least at
their core, Clark and Superman were the same person. There was a real
goodness there, even if it was clumsy and imperfect. Is there a core to
you, Lex?''

``Lois, I have a franchise of orphanages set up throughout the United
States now, headed by caring, competent people,'' said Lex. ``I am
personally spearheading a number of advancements in the sciences that
will revolutionize the world ten times over. If the United States goes
to war in the coming years, one of the reasons we will emerge victorious
is because of the vast resources that I control and the overwhelming
technological superiority that we will enjoy. I have done more to end
the Great Depression than any single other person on the planet. That is
my core.''

Lois only glared at him. She stood slowly, seeming years older than when
they'd first met. ``I wish I'd never met you,'' she said. She left
without another word.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

He'd waited too long.

Superman had been stopping by with food every three days like clockwork.
The hole in the ground had been expanded, and he'd brought in more
supplies. It was gratifying to have his pitiful existence made slightly
more bearable, but at the same time every new possession in his
miserable little hole meant that his captivity became more and more
permanent.

The plan had been to wait for Superman to make his next visit (canned
foods, refill the barrel of water, empty the waste bucket) and then make
the trip up after that so that there was less of a chance of starving to
death in the woods once he made it out of the hole, not to mention that
he needed as much time to scurry away before the big blue warden came
back to tend to his only prisoner.

It was difficult to mark time, given how close to the Arctic Circle he
was. The sun dipped down to the horizon and then stayed there. But when
three days had come and gone, Floyd had waited another two days after
that, worried that Superman was simply late. He'd let his food get too
low, and was going to have to make the climb on an empty stomach.

He was thirty feet up when he slipped. He'd been trying to lunge up to a
higher handhold, and when he missed and sank back down to let his weight
rest on his feet, one of them slipped. Then he was falling.

He lay on the cold, hard floor with a broken leg. There was no chance
that he would be able to make the climb now, let alone hike through the
wilderness. He made a quick tourniquet and a splint, and hoped that
Superman would come back.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\emph{Author's Note: Thanks for reading.}
