\chapter{Literally Incredible}\label{literally-incredible}

\emph{Author's Note: This story is rated M for adult language and
themes, including discussion of sexual violence.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Lex Luthor had been lounging in the Skylight Club when he'd first heard
of Superman.

``He's a fellow that flies through the sky!'' declared one of the
patrons, whose name Lex couldn't recall, a good sign that the man was
someone unimportant.

``Impossible,'' said Lex with a mild tone that nevertheless carried
across the room. The conversation at the table stopped, and Lex unfolded
himself from his customary chair and walked over to join the three men,
holding a martini in one hand. Lex wore a suit, one of his more casual
ones that had only cost what a dockworker made in a month. His head was
completely free of hair, save for his thick, expressive eyebrows. He was
a dashing figure, he knew, muscular and well‐proportioned, the result of
the delicate care he gave to his body. The man who had been speaking,
the one who had said that a man flew through the sky, was wearing a
charcoal grey suit that was three months out of fashion.

``Alexander Luthor,'' he said, holding out his hand. ``But everyone
calls me Lex. Now, tell me about this flying man, and I'll see what to
think of the matter.''

``Dimitri Vladkov,'' said the man. He seemed shaken, but it was
difficult to tell whether that was from the personal attention of Lex
Luthor or from whatever delusions he was apparently suffering. ``There
was this car crash down near 1st Ave and 30th Street, you could see it
comin', but all of a sudden this guy swoops down from the sky. He was
wearing a funny costume, blue tights and a red cape, with a big `S' on
his chest, and he stops these two cars from hittin' each other, moving
fast as lightnin'.''

``I see,'' said Lex with an arched eyebrow. ``And how did he fly? Did he
flap his wings, like a bird? Did he use engines, like a plane?''

``Well, I didn't see him come down Mr. Luthor, but I saw when he left,
and he just stuck his hands up in the air and lifted off, like he was
being pulled up by strings.'' He looked at Lex's face. ``Only there
weren't no strings, not that I could see, and I looked for 'em.''

``And when he stopped this car crash from happening,'' said Lex in a
calm and steady voice, ``He did so with only his hands? How would he
even have known that there was going to be a car crash?''

``I don't know how he knew it was gonna happen,'' said Dimitri. ``But he
landed right between `em and put out his hands, like he wasn't afraid of
gettin' squished, and sure enough he touched 'em like they were barely
there, slowed 'em right down, an put a dent in each of 'em.''

``So not only can this man fly, he has incredible speed and strength as
well, if what you're saying is true?'' asked Lex. His smile was so sharp
it could have cut glass.

``Well, yeah Mr. Luthor,'' said Dimitri. ``He didn't say nothin'
afterwards, just looked to make sure that the drivers were alright and
then flew away, fast as a racehorse but straight up into the sky. We had
all sorts of questions, but he didn't answer none of 'em.''

``Thank you,'' said Lex. He signaled for the barman to get Dimitri a
drink, then went back to sit in his customary chair and think.

Heavier than air flight had been given its first practical demonstration
almost two decades ago, but to do it without the assistance of a machine
was physically impossible. It was highly probable that Dimitri Vladkov
had hallucinated, or that he was simply lying for attention. Lex also
entertained the notion that the trick of flight had been accomplished by
smoke and mirrors, and that Dimitri had merely been fooled, but he
couldn't see what the point of that would be.

Lex frowned, and returned to other thoughts. Yet even as he tried to
decide what to do about Nikola Tesla, who was staying in the Hotel
Metropolis on LexCorp's dime, his thoughts returned to the improbable
story about a man who could fly. With a twitch of his fingers, he
signaled for Mercy Graves, his indispensable secretary and the only
woman allowed in the Skylight Club before the sun went down.

``A pencil and paper,'' said Lex. Mercy nodded, and from a large purse
she kept at her side produced both for him, nearly before he had asked
for them. He'd won Mercy's service in a poker game three years before,
and often wondered how he had managed without her.

It was a simple physics problem, with a high number of variables
involved, but Lex was nothing if not quick to attack a problem. He had
always liked numbers. After a few minutes of working at it, he had an
upper and lower bound estimate on the amount of force that would be
required to stop two cars from hitting each other, and another estimate
for what it would take to raise a man into the air ``as fast as a
racehorse''. He frowned at the answers.

``Mercy darling, there was very nearly a car accident near 1st Avenue
and 30th Street. Be a dear and see if you can't find me some
eyewitnesses to speak with.'' He knew it was foolish, but if money and
power didn't allow you to chase down the things that piqued your
curiosity, Lex didn't know what they were good for.

Three hours later, Lex stood at the intersection himself, looking
around. Mercy had gotten corroboration from eight witnesses, which only
raised further questions. Talking to more people would be useless,
especially since their stories had begun to contradict one another
fairly quickly. Lex took this as evidence that this wasn't some
elaborate ruse, or at least that if it was a ruse it had been
constructed by someone sufficiently intelligent. Eyewitness accounts
were notoriously unreliable, but most people didn't know this, and so
someone running a confidence scheme of some sort would likely have had
the confederates agree on a story. Lex looked down at the street, which
showed some patches of rubber where the cars had skidded, then up at the
sky. It might have been possible to do it with ropes and wires, though
nearly impossible to hide.

There was a type of elastic rope known as a bungee, and if you could
time it absolutely perfectly, you might be able to drop down and appear
right between two cars, touching the ground just as you reached zero
velocity. From there, you could use a harness and carabiners to clip on
to something while everyone was distracted by an elaborate costume. That
would make ``flying'' as simple as unclipping again and allowing the
elastic to propel you skywards. It would be delicate work, and
incredibly dangerous, but Lex had seen enough Charlie Chaplin films to
know that sometimes people did delicate and dangerous things simply for
the benefit of an audience and a small amount of money. That left the
question of hiding the ropes themselves, which would be no easy task,
even if the ropes were quite small, and you would also need a large
number of people to be complicit, which would further complicate things,
and all to accomplish what? It reminded Lex of a magic trick, and Lex
hated magic tricks, at least until he figured out how they were done.
After ten minutes of looking around, Lex grit his teeth. Mercy, standing
just behind him, politely coughed.

``You're right,'' said Lex. ``Enough time wasted on this distraction.''
He forced a smile. ``Put out the proper feelers. If someone tries this
stunt again, I want to know about it.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

``He came outta nowhere,'' said Little Tony.

Lex gave the man a sympathetic nod. ``Tell me about him.''

``We was robbin' the jewelry store,'' said Little Tony. ``An he came
outta nowhere, left the door spinnin' behind him.'' Little Tony was a
giant of a man, ironically named by his fellow thugs who considered that
the height of wit.

Lex Luthor had gone legitimate five years ago. Oh, he hired goons from
time to time for various bits of dirty work and still maintained
contacts in the criminal underworld, as well as receiving cash into a
slush fund from enterprises that he'd set in motion long ago~---
whorehouses, fighting rings, smuggling operations, and things of that
nature~--- but the fund was never touched by him, and existed only in
case there was an emergency. But for the most part, the crimes that Lex
Luthor was guilty of were white collar crimes, the kind that it would
take a forensic accountant or highly trained lawyer to unravel, and even
those he didn't do too often. Lex didn't see the need to run underground
gambling dens when he could get a special piece of legislation passed
that would allow an exclusive permit for a casino on the outskirts of
Metropolis. There was no need to be a criminal when you could get the
law to work for you.

Little Tony worked for Willie Calhoun, one of the largest crime bosses
in Metropolis and a former mentor to Lex Luthor. Lex and Willie had
parted ways amicably around the time that Lex was picking up his first
doctorate, but they'd always kept in touch, and occasionally they would
call in favors. Lex was talking to Little Tony in a small room lit by a
bare bulb as the result of one of these favors, as well as a promise to
pay for Little Tony's legal expenses. The large man was currently out on
bail.

``Leroy spun around and shot at him,'' said Little Tony. ``But the guy
moved as fast as lightning, and had his hand around tha barrel of tha
shotgun before it even went off.''

``Was there a thunderclap?'' asked Lex.

Little Tony scratched his head.

``Was there a loud sound that accompanied his movements?'' Lex asked. He
was out of practice in dealing with people like Little Tony. That had
once been his whole life.

``Nah,'' said Little Tony. ``Just like a little breeze, you know?'' Not
nearly as fast as lightning then, just a turn of phrase that people
seemed to like using.

``Leroy missed then?'' asked Lex.

``No,'' said Little Tony, shaking his head. ``Hit him square inna chest
with the full load.''

Lex frowned.

``I'm tellin' a truth,'' said Little Tony. ``Buckshot bounced offa him
like it were nothin'.''

``Did it tear the costume?'' asked Lex.

``The suit?'' asked Little Tony. Lex nodded. ``Yeah, tore it right up,
ripped it good. How'd you know?'' Lex hadn't known, he'd just been
asking, but it wouldn't do to tell Little Tony that.

``Continue on,'' said Lex.

``Well, this guy takes Leroy's shotgun right outta his hands, bends it
in two, and drops it to the floor. Guy just got shot in the chest an
acts like he didn't even notice. He looks at me and says that we're
under arrest, an' I tell him he ain't no cop, an' he says somethin'
about a citizen's arrest. An' as he's goin' on 'bout how he's got a
legal power or whatever, I rush him. That weren't too smart, because
before I know it I'm on my back.'' Little Tony rubbed the back of his
head and let out a sigh.

``Could you see him move?'' asked Lex. ``When he fought back?''

``Sure,'' said Little Tony. ``An' he didn't hurt me none. It was like I
was a little kid to him. All of a sudden I was flipped around and laid
out on the ground, gentle like he was worried about hurtin' me. Then we
just waited for the police to come, since Leroy and I didn't wanna try
our luck again. This guy, he gives the police a salute, didn't talk
about nothin' but the robbery even though they had all sorts of
questions for him, and then flew off.''

Lex frowned. ``One final question. How did he know about the robbery?''

``He musta seen us go in,'' said Little Tony, scratching his head.

``Do you know how rare crime is in Metropolis, all things considered?
The idea that he would just happen to be in the neighborhood and spot
you go into the jewelry store is~--- well, not inconceivable, but
significantly unlikely enough that I'm not willing to credit it as
plausible.'' Especially not given the other reports that were coming in.
Lex stood up from the table. ``Thank you for your time. A lawyer will be
in touch.''

Willie Calhoun was waiting outside the room. ``If it isn't my favorite
egghead,'' he said with a smile. Willie was in his late fifties now, and
had grown fat and soft. He was no longer the terrifyingly muscular man
that had trained Lex to fight, cheat, and steal.

``Willie,'' said Lex. They spoke as equals now, which both considered a
mark of respect for the other.

``What are we dealing with here?'' Willie asked. ``Some guy shows up in
tights and starts hassling my boys?''

``This is bigger than you,'' said Lex. ``Bigger than Metropolis even.
Lay low for the time being. Call off any jobs you have planned.''

``I've got mouths to feed,'' said Willie. ``I can't just slam on the
brakes.''

``He's stronger and faster than anything the world has seen before,''
said Lex. ``He can fly. And unless you've been unusually sloppy, he has
some way to learn about crimes as they're happening. Stop everything
until you know more. I've tracked five separate instances today, and you
can be damned sure there will be more.''

``You're with us on this one?'' asked Willie. ``We need your brains.''

``No,'' said Lex. ``Like I said, this is big. Bigger than the city.
Maybe the biggest thing that's ever happened in the history of the human
race. I may call in a few favors trying to get a handle on it, but rest
assured even if I'm not with you, we're working towards the same goal
for the time being.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The interview came out the next week.

``It makes no sense,'' said Lex Luthor, setting down the paper.

``Why not?'' asked Mercy from her desk.

Lex pointed directly at the offending line. ``\,`Superman told me that
he was an alien from the planet Krypton, the last of his kind.'\,'' read
Lex. ``He's an alien, or so he claims, yet he looks just like a human.''
Lex lifted the paper to show to Mercy. On the front of The Daily Planet
was a picture, with Superman standing right next to Lois Lane. The
headline read ``Exclusive Interview With The Man of Steel''.

``Now then,'' said Lex, ``I will admit that a degree of convergence is
implied by Darwin's theory of evolution, but not to such an extent.
These features, a strong jaw and brown hair, blue eyes and his
ridiculous musculature, well, I can accept that the marsupials of
Australia bear more than a passing resemblance to the more traditional
mammals of North America despite being separated by millions of years,
but this beggars belief. And why does he even need legs if he can fly?
What evolutionary reason would there even be for that? And not only does
he look human, but he looks like an attractive human at that!''

``Do you think he's lying?'' asked Mercy. Boredom was apparent in her
voice. She was possessed of a disinterested character, one that Lex
found quite pleasing. He never had to worry about what Mercy thought,
and never had to engage her in unwanted conversation. She was there for
him to bounce his thoughts off of, and she knew it, which was what made
the whole arrangement work. Before she'd come under his employ, Lex had
muttered to himself, which didn't feel nearly so good as speaking aloud
to someone. It helped that Mercy was one of the few people that Lex
could treat as trusted.

``I don't know,'' Lex answered. ``I need more data. Certainly there are
things he says that are inconsistent with reality as I knew it, yet if
you had asked me a year ago whether I would see a man like Superman who
can bend steel with his hands and fly through the air, I would have been
tempted to fire you for expressing such sheer stupidity. Obviously
something that I thought was true about the universe is not.'' He looked
back down at the newspaper.

``And here!'' he practically shouted, pointing at another offending
sentence. ``Here he claims that he can hear a gunshot from across the
city. It's ludicrous, sound doesn't travel that far, and even if his
ears were as sensitive as his muscles are powerful, a gunshot would fade
in with the background noise. He's not only claiming that he can hear
things from two dozen miles away, but that he can further distinguish
those sounds from all the other sounds happening in the city at any
given moment. And yet how else can we explain what's been observed? He
really does dart across the city at just below the speed of sound,
flying through the air at these incredible velocities, going right where
he thinks he's needed. And it's not just that he can hear things he
shouldn't be able to, it says here that he can see through walls and
watch for criminal activities from miles away. It should be literally
incredible~--- not worthy of credit. And yet based on what we can
observe of him, he seems to be telling the truth, at least about his
abilities if not his origin.'' He turned to look at Mercy. ``How do you
feel about him?'' asked Lex.

``Feel, sir?'' asked Mercy, stirring slightly in her seat but by no
means looking uncomfortable. Lex had never seen Mercy look
uncomfortable.

``If he's telling the truth, he can hear everything that we're saying
right now. He can watch us as we speak. When you change your clothes or
take a bath, he can look in on you.'' Mercy was nearly as beautiful as
she was competent, though she kept up a rather severe look most of the
time, with her hair tied back in a neat bun and her skirts with perfect
pleats that fell well below the knee.

``He's doing good,'' said Mercy. She always gave her honest opinion when
he asked it of her, without hesitation, which was another reason she was
so valuable to him. ``I imagine that he's too much of a hero to watch
me.''

``He's a hero,'' said Lex. ``For now.'' He looked down at a pad of
paper, where he'd been making revisions to his estimates. ``I've run the
numbers. Even using the lower bounds for his strength and speed, if he
ever decided that he wasn't a hero anymore, he could demolish this city
in the space of three hours, down to the last man, woman and child. If
we're just talking about the central business district, he could do it
in three minutes. He\==='' Lex stopped. ``He can hear everything that we
say. He can watch us. He can read the files that are sitting in my
drawers. Before anything else, I think it's time to clean house.''
